Gradient-boosted equivalent sources

### 2021-01-28 manuscript/manuscript.tex
Start editing manuscript to work with GJI style

\documentclass[twocolumn]{article}
%\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[longend,linesnumbered,ruled]{algorithm2e}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round,authoryear,sort]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{setspace}

@@

% Define special units
\DeclareSIUnit\mgal{\milli Gal}

@@

% Import files with parameter values generated by notebooks
\newcommand{\Gal}{Gal}
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}
\input{boost-overlapping.tex}
\input{australia.tex}

% Define title, authors, affiliations and DOI
% ===========================================
\newcommand{\Title}{%
    Gradient-boosted equivalent sources
}
\newcommand{\Author}{%
    S.R. Soler,
    L. Uieda
}
\newcommand{\AuthorAffil}{%
    {\large
        Santiago R. Soler$^{1,2}$,
        Leonardo Uieda$^{3}$
    }
    \\[0.4cm]
    {\small $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com)} \\
    {\small $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina} \\
    {\small $^{3}$Department of Earth, Ocean and Ecological Sciences, School of Environmental Sciences, University of Liverpool, UK} \\
}
\newcommand{\DOI}{%
    doi:\href{https://doi.org/xxx.xxx/xxxxxx}{xxx.xxx/xxxxxx}
}
\newcommand{\DOILink}{%
    \href{https://doi.org/xxx.xxx/xxxxxx}{doi.org/xxx.xxx/xxxxxx}
}

% Configure header and hypersetup
% ===============================
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{} (\the\year{}). \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    \today
}
\maketitle

\noindent
\textbf{Keywords:}
Gravity anomalies and Earth structure;
Magnetic anomalies: modelling and interpretation;
Geopotential theory;
Inverse theory;
Statistical methods;
Australia;

\begin{abstract}
  The equivalent source technique is a powerful and widely used method for
  processing gravity and magnetic data.  Nevertheless, its major
  drawback is the large computational cost in terms of processing time and
  computer memory.
  We present two techniques for reducing the computational cost of equivalent
  source processing: block-averaging source locations and the
  gradient-boosted equivalent source algorithm.
  By using block-averaging, we reduce the number of source coefficients that
  must be estimated while retaining the minimum desired resolution in the final
  processed data.
  With the gradient boosting method, we estimate the layer coefficients in
  small batches along overlapping windows, allowing us to reduce the computer
  memory requirements arbitrarily to conform to the constraints of the
  available hardware.
  We show that the combination of block-averaging and gradient-boosted
  equivalent sources are capable of producing accurate interpolations through
  tests against synthetic data.
  Moreover, we demonstrate the feasibility of our method by gridding a gravity
  dataset covering Australia with over 1.7 million observations using a modest
  personal computer.
\end{abstract}

@@

\bibliographystyle{humannat}
\bibliography{references}

>>>>

\documentclass[extra]{gji}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[longend,linesnumbered,ruled]{algorithm2e}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{setspace}

@@

% Define special units
\DeclareSIUnit\mgal{\milli Gal}
\newcommand{\Gal}{Gal}

@@

% Import files with parameter values generated by notebooks
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}
\input{boost-overlapping.tex}
\input{australia.tex}

% Define title, authors and affiliations
% ======================================
\title{
    Gradient-boosted equivalent sources
}
\author[S.R. Soler and L. Uieda]{
    Santiago R. Soler$^{1,2}$ and Leonardo Uieda$^3$ \\
    $^{1}$CONICET, Argentina (santiago.r.soler@gmail.com) \\
    $^{2}$Instituto Geofísico Sismológico Volponi, UNSJ, Argentina \\
    $^{3}$Department of Earth, Ocean and Ecological Sciences, School of
    Environmental Sciences, University of Liverpool, UK
}

@@

\maketitle

\begin{summary}
  The equivalent source technique is a powerful and widely used method for
  processing gravity and magnetic data.  Nevertheless, its major
  drawback is the large computational cost in terms of processing time and
  computer memory.
  We present two techniques for reducing the computational cost of equivalent
  source processing: block-averaging source locations and the
  gradient-boosted equivalent source algorithm.
  By using block-averaging, we reduce the number of source coefficients that
  must be estimated while retaining the minimum desired resolution in the final
  processed data.
  With the gradient boosting method, we estimate the layer coefficients in
  small batches along overlapping windows, allowing us to reduce the computer
  memory requirements arbitrarily to conform to the constraints of the
  available hardware.
  We show that the combination of block-averaging and gradient-boosted
  equivalent sources are capable of producing accurate interpolations through
  tests against synthetic data.
  Moreover, we demonstrate the feasibility of our method by gridding a gravity
  dataset covering Australia with over 1.7 million observations using a modest
  personal computer.
\end{summary}

\begin{keywords}
Gravity anomalies and Earth structure,
Magnetic anomalies: modelling and interpretation,
Geopotential theory,
Inverse theory,
Statistical methods,
Australia,
\end{keywords}

@@

\bibliographystyle{gji}
\bibliography{references}
